Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2021-05-15 paper/intro.tex
Restored Distribution Statement, other DARPA public approval boilerplate

The DARPA Cyber Assured Systems Engineering (CASE) program is targeted at developing tools for design, analysis, and verification that enable systems engineers to {\em design-in} cyber-resiliency for complex cyber-physical systems.
%\footnote{The
%  views expressed are those of the authors and do not reflect the
%  official policy or position of the Defense Advanced
%  Research Projects Agency (DARPA) or the U.S. Government.}
We have developed a Model-Based Systems Engineering (MBSE) environment called {\em BriefCASE} which is based on the Architecture Analysis and Design Language (AADL)~\cite{aadl}.  BriefCASE extends the Open Source AADL Tool Environment (OSATE) to add new design, analysis, and code generation capabilities for building cyber-resilient systems.

>>>>

The DARPA Cyber Assured Systems Engineering (CASE) program is targeted at developing tools for design, analysis, and verification that enable systems engineers to {\em design-in} cyber-resiliency for complex cyber-physical systems.\footnote{This work was funded in part by the Defense Advanced Research Projects Agency (DARPA).  The views expressed are those of the authors and do not reflect the official policy or position of DARPA or the U.S. Government.}
We have developed a Model-Based Systems Engineering (MBSE) environment called {\em BriefCASE} which is based on the Architecture Analysis and Design Language (AADL)~\cite{aadl}.  BriefCASE extends the Open Source AADL Tool Environment (OSATE) to add new design, analysis, and code generation capabilities for building cyber-resilient systems.

### 2021-05-15 paper/paper.tex
Add clearpage for appendix
Merge overleaf
Restored Distribution Statement, other DARPA public approval boilerplate

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\usepackage{paralist}
\usepackage{graphicx}
\graphicspath{{./figs/}} 
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

@@

\begin{document}
\title{
  Synthesizing Verified Components for Cyber Assured Systems Engineering 
  \thanks{{This work was funded by DARPA contract HR00111890001. The
views, opinions and/or findings expressed are those of the authors
and should not be interpreted as representing the official views or
policies of the Department of Defense or the U.S. Government.}
  }
}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Eric Mercer}
\IEEEauthorblockA{Department of Computer Science\\
Brigham Young University\\
Provo, Utah}
\and
\IEEEauthorblockN{
Konrad Slind, \\
Isaac Amundson and
Darren Cofer}
\IEEEauthorblockA{
Applied Research and Technology\\
Collins Aerospace\\
Minneapolis, Minnesota}
\and
\IEEEauthorblockN{
Junaid Babar, David Hardin}
\IEEEauthorblockA{
Applied Research and Technology\\
Collins Aerospace\\
Cedar Rapids, Iowa}
}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

\section{Introduction}
\input{intro}

\section{Simple Example}
\input{example}

\section{AGREE Contract Specification}
\input{agree}

\section{Synthesis}
\input{synthesis}

\section{UxAS Case Study}
\input{case-study}

\section{Related Work}
\input{related-work}

\section{Conclusion}
\input{conclusion}

@@

% references section
\bibliographystyle{IEEEtran}
\bibliography{paper}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{comment}
\usepackage{paralist}
\usepackage{graphicx}
\graphicspath{{./figs/}} 
\usepackage{listings}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{flushend}

@@

\begin{document}
\title{
  Synthesizing Verified Components for Cyber Assured Systems Engineering 
  \thanks{DISTRIBUTION STATEMENT A.  Approved for public release.}
}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Eric Mercer}
\IEEEauthorblockA{Department of Computer Science\\
Brigham Young University\\
Provo, Utah}
\and
\IEEEauthorblockN{
Konrad Slind, Isaac Amundson, Darren Cofer}
\IEEEauthorblockA{
Applied Research and Technology\\
Collins Aerospace\\
Minneapolis, Minnesota}
\and
\IEEEauthorblockN{
Junaid Babar, David Hardin}
\IEEEauthorblockA{
Applied Research and Technology\\
Collins Aerospace\\
Cedar Rapids, Iowa}
}
% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

@@

\section{Introduction} \label{sec:intro}
\input{intro}

\section{Simple Example} \label{sec:example}
\input{example}

\section{AGREE Contract Specification} \label{sec:agree}
\input{agree}

\section{Synthesis} \label{sec:synthesis}
\input{synthesis}

\section{UxAS Case Study} \label{sec:case-study}
\input{case-study}

\section{Related Work} \label{sec:related-work}
\input{related-work}

\section{Conclusion} \label{sec:conclusion}
\input{conclusion}

@@

% references section
\clearpage
\bibliographystyle{IEEEtran}
\bibliography{paper}
